---
output: github_document
---

# dutchmasters

This package offers six color palettes derived from paintings by the Dutch
masters Johannes Vermeer and Rembrandt van Rijn. This package is inspired by
the [`ochRe` package](https://github.com/ropenscilabs/ochRe/) and functions
from this package have been shamelessly copied. The list 
`dutchmasters::dutchmasters` contains six named character vectors with color
codes. The names represent the colors and where on the painting the color was
taken.

```{r}
library(dutchmasters)
dutchmasters$anatomy
```

## Examples

```{r}
library(ggplot2)
ggplot(diamonds, aes(color, fill = clarity)) +
  geom_bar() +
  scale_fill_dutchmasters(palette = "staalmeesters")
```

```{r}
ggplot(mtcars, aes(disp, mpg, col = qsec)) +
  geom_point(size = 4) +
  scale_color_dutchmasters(discrete = FALSE)
```

The six available palettes are

Vermeer -[*The Milkmaid*](https://en.wikipedia.org/wiki/The_Milkmaid_(Vermeer))

```{r}
ochRe::viz_palette(dutchmasters$milkmaid)
```

Vermeer -[* Girl with a Pearl Earring*](https://en.wikipedia.org/wiki/The_Milkmaid_(Vermeer))

```{r}
ochRe::viz_palette(dutchmasters$pearl_earring)
```

Vermeer - [*View of Delft*](https://en.wikipedia.org/wiki/View_of_Delft)

```{r}
ochRe::viz_palette(dutchmasters$view_of_Delft)
```

Vermeer - [*The Little Street*](https://en.wikipedia.org/wiki/The_Little_Street)

```{r}
ochRe::viz_palette(dutchmasters$little_street)
```

Rembrandt - [*The Anatomy Lesson of Dr. Nicolaes Tulp*](https://en.wikipedia.org/wiki/The_Anatomy_Lesson_of_Dr._Nicolaes_Tulp) 

```{r}
ochRe::viz_palette(dutchmasters$anatomy)
```

Rembrandt - [*The "Staalmeesters"*](https://en.wikipedia.org/wiki/Syndics_of_the_Drapers%27_Guild)

```{r}
ochRe::viz_palette(dutchmasters$staalmeester)
```

## Installation

You can install `dutchmasters` from github with:

```{r, message=FALSE}
devtools::install_github("EdwinTh/dutchmasters")
```

